EasyMerge - A New Tool for Code Clones Refactoring

### 2014-03-17 paper/paper.tex
paper update
paper updates

\section{EasyMerge}
\subsection{User Interface}

\subsection{Preprocessing}

>>>>

\section{EasyMerge}
The entire EasyMerge program is written with Python 2.7.5 and the user interface is powered by PyQt 4.10.4.
It takes a folder of Python written source tree as input, look for all refactorable clones and recommend potential merges.

\subsection{User Interface}
EasyMerge has a simple and straightforward user interface, as shown in figure.

\subsection{Preprocessing}
The first step of EasyMerge is to run CloneDigger at target source tree, take its output and format and standardize it for our own usage.
The core of this step is to classify code clones and get the ones that we not only can but also want to merge.
